A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-09 main.tex
Updates from Overleaf

\subsubsection{TCIA validation}
%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
image-based phenotypes and their underlying genomic data 
%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
%https://github.com/Serian1992/ImgBio.

@@

https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
#XAI
Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data

@@

https://www.deeplearningbook.org/
https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
% NCI
Aiding the Genomic Characterization of Tumors: 
deep learning could predict commonly mutated genes and mRNA expression from the images
*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
Preprocessing of whole-slide images. The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets. We divided the whole-slide images into squares of 112 × 112 μm (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background. We sampled a maximum of 8000 such tiles from each slide. We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster. The use of these supertiles reduces the dimensions of a slide to 100 × 2048. The model was first trained on this reduced dataset, with all the TCGA data. Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.

@@

%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk. Updated: August 31, 2020
%
TMA by deep learning (CNN) mRNA expression associated with pathological images
*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
recurrent neural network for NLP

@@

%% TCGA new holistic features %%%%%
In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_mrna$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

>>>>

\subsubsection{TCIA validation by deep learning}
%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
image-based phenotypes and their underlying genomic data 
%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
%https://github.com/Serian1992/ImgBio.

@@

%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
#XAI
Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data

@@

%https://www.deeplearningbook.org/
%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
% NCI
Aiding the Genomic Characterization of Tumors: 
deep learning could predict commonly mutated genes and mRNA expression from the images
*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
Preprocessing of whole-slide images. The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets. We divided the whole-slide images into squares of 112 × 112 μm (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background. We sampled a maximum of 8000 such tiles from each slide. We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster. The use of these supertiles reduces the dimensions of a slide to 100 × 2048. The model was first trained on this reduced dataset, with all the TCGA data. Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.

@@

%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk. Updated: August 31, 2020
%
TMA by deep learning (CNN) mRNA expression associated with pathological images
*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
%recurrent neural network for NLP

@@

%% TCGA new holistic features %%%%%
In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
